I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-24 Paper/Paper_noProof.tex
intro
table 6 may be.

\vspace{-0.4cm}
\begin{figure}[h!]
	\centering
\begin{tikzpicture}
	\begin{axis}[width=12cm,height=6cm,
		xlabel={},
		ylabel={},
		title={runtime (seconds per node)},
		legend pos=north west,
		ymin=0,
		xtick={1,2,3,4,5}, 
		xticklabels={$5\times 100$, $8\times 100$, $5\times 200$, $8\times 200$, $6\times 500$},
		]

@@

>>>>

\vspace{-0.4cm}
\begin{figure}[h!]
	\centering
\begin{tikzpicture}
	\begin{axis}[width=10cm,height=5cm,
		xlabel={},
		ylabel={},
		title={runtime (seconds per node)},
		legend pos=north west,
		ymin=0,
		xtick={1,2,3,4,5}, 
		xticklabels={$5\times 100$, $8\times 100$, $5\times 200$, $8\times 200$, $6\times 500$},
		]

@@

\begin{table}[]
	\centering
	\begin{tabular}{|c|c|cc||cc||c|}
		\hline
		\text{DNN}  & DeepPoly &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (refinedBaB) \,}} & 
		\multicolumn{2}{@{}c@{}|}{\text{ \color{blue}Comp (slow) \,}}
		& Upper\\ 
		& / CROWN & TO=300s & TO=3000s & {\color{blue}adapt} & {\color{blue}fixed} & Bound\\
		\hline \hline
		$8\times200$\  &   $25\%$? & $72\%$? & $75\%$? & {\color{blue}$75.5\%$?}  & {\color{blue}$\mathbf{77\%}$} & $89\%$? \\ 
		$\epsilon = 0.015$ & 17s & 95s? & 500s? & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
	\end{tabular}
	\caption{WIP! $\%$ of verified images over 200 images. To see how refined BAB scale with TimeOut.}
	\label{tab:example3}
\end{table}
